Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-20 doc/GMP2015/s07_problempinning.tex
Changed proof of algo. Corrected references. Increased references in intro. Changed complexity of algo throughout paper. Added citation in intro. Other smaller changes.

\begin{proof}
    We can replace each body that has only one pin by a single vertex. A
    body with 2 pins can be replaced by an edge. In general, a body with $n$
    pins can be replaced by a 2-tree on $n$ vertices. When finding a
    DR-plan, we treat each body as trivial, so they become the leaves of our
    plan. The optimal recombination problem and approach of Section
    \ref{sec:recomb} are unchanged. The optimal completion via the optimal modification problem in
Section \ref{sec:recomb} now has an additional constraint that all edges in the 2-tree representation of the bodies must be removed together, not individually.
\end{proof}

@@

\begin{observation}
\label{obs:bodypin_drp}
    For the 1-dof body-pin graphs described above, a $(3,4)$-sparsity corresponds to a canonical DR-plan whose nodes satisfy one of the following, either
    (a) the children are 2 proper vertex maximal 1-dof graphs that intersect on another 1-dof graph, or
    (b) the children are a number of proper maximal 1-dof sub-graphs, sharing at most one body.
\end{observation}

@@

The strong Church-Rosser property holds making all canonical DR-plans
optimal:
%
\begin{remark}\label{rem:1dofcanon}
    When the input is independent,
    all $(3,4)$-tight canonical DR-plans are optimal. We can find such a
    DR-plan in the same time complexity as the $(2,3)$-tight case for bar
    and joint graphs discussed in Section \ref{sec:DRP}.
    This is because
    such $(3,4)$-tight graphs are matroidal and have a pebble game, shown in \cite{Lee:2007:PGA}.
\end{remark}

\begin{figure*}\centering
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.2\linewidth}\centering
    \input{img/tikz/bodypin_graph.tikz}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.35\linewidth}\centering\scriptsize
    \input{img/tikz/bodypin_drp.tikz}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin2}
    \caption{}
\end{subfigure}
%
\caption{(a) is a 1-dof body-pin graph. (b) is the corresponding body-bar graph explained in Definition \ref{def:body-pin}. (c) is the 1-dof DR-plan for the graph. In this case, to obtain an isostatic system, we would need to add a body and 2 pins to one of the nodes in the second level. (d) is the result of adding one such body to the bold-faced node.}
%
\end{figure*}
The above discussion leads to the main theorem:
\begin{theorem}
\label{thm:1dofcase}
    Given a 1-dof body-pin or triangle-multipin graph $G$ and corresponding
    1-dof DR-plan $T$, there is a quadratic algorithm for the 1-dof optimal
    completion problem of Section \ref{sec:recomb}.
\end{theorem}

>>>>

@@

\begin{observation}
\label{obs:bodypin_drp}
    For the 1-dof body-pin graphs described above that are $(3,4)$-sparse, a $(3,4)$-tight canonical DR-plan exists where every node of a $(3,4)$-sparse graph satisfies one of the following: (1) its children are 2 proper vertex maximal 1-dof graphs that intersect on another 1-dof graph; or (2) its children are all of the proper maximal 1-dof sub-graphs, pairwise sharing at most one body.
\end{observation}

% \begin{observation}
% \label{obs:bodypin_drp}
%     For the 1-dof body-pin graphs described above, $(3,4)$-sparsity corresponds to a canonical DR-plan whose nodes satisfy one of the following, either
%     (a) the children are 2 proper vertex maximal 1-dof graphs that intersect on another 1-dof graph, or
%     (b) the children are a number of proper maximal 1-dof sub-graphs, sharing at most one body.
% \end{observation}

@@

The strong Church-Rosser property holds making all canonical DR-plans
optimal:
%
\begin{remark}\label{rem:1dofcanon}
    When the input is independent,
    all $(3,4)$-tight canonical DR-plans are optimal. We can find such a
    DR-plan in the same time complexity as the $(2,3)$-tight case for bar-joint graphs discussed in Section \ref{sec:DRP}.
    This is because
    such $(3,4)$-tight graphs are matroidal and have a pebble game, shown in \cite{Lee:2007:PGA}.
\end{remark}

\begin{figure*}\centering
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.2\linewidth}\centering
    \input{img/tikz/bodypin_graph.tikz}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.35\linewidth}\centering\scriptsize
    \input{img/tikz/bodypin_drp.tikz}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin2}
    \caption{}
\end{subfigure}
%
\caption{(a) is a 1-dof body-pin graph. (b) is the corresponding body-bar graph explained in Definition \ref{def:body-pin}. (c) is the 1-dof DR-plan for the graph. In this case, to obtain an isostatic system, we would need to add a body and 2 pins to one of the nodes in the second level. (d) is the result of adding one such body to the bold-faced node.}
%
\end{figure*}
The above discussion leads to the main theorem:
\begin{theorem}
\label{thm:1dofcase}
    Given a 1-dof body-pin or triangle-multipin graph $G$ and corresponding
    1-dof DR-plan $T$, there is an \candrpcomplexity algorithm for the 1-dof optimal
    completion problem of Section \ref{sec:recomb}.
\end{theorem}

### 2014-12-20 doc/GMP2015/s09_conclusion.tex
Changed proof of algo. Corrected references. Increased references in intro. Changed complexity of algo throughout paper. Added citation in intro. Other smaller changes.

We have clarified the main source of complexity for the optimal DR-plan and recombination problems. For the former problem, when there are no overconstraints, (as is the case for 2D qusecs whose realizations are many common types of layered materials), we defined a canonical DR-plan and showed that such canonical DR-plans are guaranteed to be optimal, a strong Church-Rosser property giving an efficient ($O(n^2)$) algorithm to find an optimal  DR-plan that satisfies other desirable characteristics.

>>>>

We have clarified the main source of complexity for the optimal DR-plan and recombination problems. For the former problem, when there are no overconstraints, (as is the case for 2D qusecs whose realizations are many common types of layered materials), we defined a canonical DR-plan and showed that such canonical DR-plans are guaranteed to be optimal, a strong Church-Rosser property giving an efficient (\candrpcomplexity) algorithm to find an optimal  DR-plan that satisfies other desirable characteristics.
